\documentclass{article}

    \usepackage[margin=1in]{geometry}
    \usepackage{hyperref}
    \usepackage{listings}
    \lstset{
        breaklines = true,
        language = SQL,
        numbers = left,
        basicstyle = \footnotesize
    }

    \title{Lesson Plan 13, ISTA-420}
    \author{Chapter 8, T-SQL Fundamentals}
    \date{June 20, 2017}

\begin{document}    

    \maketitle{}

    \section{Class Discussion}

    Pages: 266 --- 287

    \begin{enumerate}
        \item The sales tax rate for a state just changed. How would you update the state sales tax table to reflect the changes? Assume that this table has an ID column, an RATE column, and a STATE column.
        \item The Revenue Division has requested that you provide a report on what the actual sales taxes would have been for all orders in the past year, assuming the retroactivity of the new sales tax rate. How would you calculate this?
        \item Explain how the proprietary assignment update command works.
        \item What is one very important purpose of the MERGE SQL statement? What is ETL (not in book)?
        \item What are the semantics of MERGE?
        \item Write a typical INSERT OUTPUT statement.
        \item Write a typical UPDATE OUTPUT statement.
        \item Write a typical DELETE OUTPUT statement.
        \item Write a typical MERGE OUTPUT statement.
        \item What is nested DML?
    \end{enumerate}

    \section{In Class Exercises}


    \begin{enumerate}
\item Look at the csv file named presidents-short.csv in the SQL directory. Create an appropriate table schema.

\item Insert the CSV data into the table you just created.

\item Delete the first record from your table using the output clause. This is the header.

\item Alter the presidents table by adding a primary key column .

\item Bring the data up to date by updating the last row and adding a new row. Use the output clause.

\item Alter the presidents table to update the current party names, use the output clause.  Federalists and Whigs became Republicans.  Democratic-Republicans became Democrats
    \end{enumerate}

    \section{Graded Labs}

    LearnOnDemand lab 8.

    \section{Course Project}

    Iteration 3 design phase.

    \section{Homework}

        Read chapter 9, pages 297  -- 313  in the \textit{T-SQL Fundamentals} book.
        

\end{document}    
